MixEth: efficient, trustless coin mixing service for Ethereum

### 2018-12-20 article/shortpaper/main.tex
Added ae package to for clearer fonts
Small edits to the short paper

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{authblk}
\usepackage{booktabs}
%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

@@

\begin{abstract}
Cryptocurrencies enable users to transact pseudonymously with each other without relying on trusted parties or intermediaries. These transactions are recorded in an immutable, publicly verifiable ledger. Due to the ledger's transparent nature, privacy is notably reduced. If the link between users' public key and their physical identity is exposed, their pseudonymity is lost. One way to increase users' privacy is to deploy coin mixing services. In this paper, we present MixEth, which is a trustless coin mixing service. MixEth is more efficient than any proposed trustless coin tumbler. It requires only $3$ on-chain transactions at most per user and $1$ off-chain message. It achieves strong notions of anonymity and is able to resist denial-of-service attacks. Furthermore the underlying protocol can also be used to efficiently shuffle ballots, cyphertexts in a trustless and decentralized manner.     
\end{abstract}
\keywords{Cryptography, Verifiable shuffle, Ethereum, Privacy, Coin mixer, State Channel}

\section{Introduction}
One of the methods to increase cryptocurrency users' privacy is coin mixing or tumbling. This technique provides \textit{k-anonymity} or \textit{plausible deniability}. The idea is that $k$ users deposit $1$ coin each and then in the course of a coin shuffling protocol either a centralized trusted third party or a smart contract mixes the coins and redistributes them to designated fresh public keys. This powerful technique gives users superior privacy and anonimity since their new received coins can not be linked to them.

@@

The two major techniques to provide decentralized mixing services for Ethereum are Möbius, a ring-signature-based solution \cite{meiklejohn2018mobius} and Miximus, a zkSNARK-based proposal \cite{miximus2018}. Both of them burn tremendous amounts of gas to withdraw funds, which could be prohibitive for many use cases. Möbius requires $\num[group-separator={,}]{335714}n$ gas ($n$ is the ring size) while Miximus consumes $\num[group-separator={,}]{1903305}$ gas to verify a zkSNARK proof \cite{miximus2018gascost}.

\textbf{Our contributions.} In this paper, we present a trustless and efficient mixing protocol for Turing-complete blockchains. To show the practicality of the protocol, we introduce MixEth, a privacy-enhancing protocol and a practical tool for Ethereum, to overcome the above mentioned efficiency issues of Ethereum-based coin-mixers while retaining strong notions of anonymity, mixer availability and theft prevention already achieved by previous proposals (\cite{meiklejohn2018mobius},\cite{miximus2018}). MixEth requires as few off-chain messages and on-chain transactions as Möbius and Miximus, meanwhile it burns significantly less gas.

We also implement MixEth in a state channel to leverage the scalability and instant finality of off-chain scaling solutions. Furthermore, the MixEth protocol could be used in any state channel application to mix funds before going back on-chain.

\section{Background}
\subsection{Notations}
Let $[]$ denote the empty tuple. For a tuple $t=(x_1,\dots,x_n)$ we denote as $t[x_i]$ the value stored at $x_{i}$. The cardinality of a finite set $X$ is denoted as $|X|$. In the following let $\lambda \in \mathbb{N}$ be the security parameter and its unary representation is $1^{\lambda}$. If $x$ is uniformly randomly sampled from a set $A$ we write $x\stackrel{\$}{\leftarrow}A$. The symmetric group of degree $n$ is written as ${S}_n$. In a cyclic group $\mathbb{G}$, the standardized generator is denoted as $G$ and we use the additive notation. Secret keys and public keys are denoted as $sk$ and $pk$ respectively (or often times $s$ and $sG$), while the user the corresponding key belongs to is indicated in subscript. Let $PK_{i}$ denote the set of public keys belonging to receivers at a particular shuffling round $i$.

@@

The Decision Diffie-Hellman assumption (DDH) is a standard cryptographic hardness assumption which underlies the security of many cryptographic protocols. Roughly speaking DDH states that no efficient algorithm can distinguish between the two distributions $(aG, bG, abG)$ and $(aG, bG, cG)$, where $a,b,c\stackrel{\$}{\leftarrow}\mathbb{Z}_{|\mathbb{G}|}$. It is believed that the DDH assumption holds for elliptic curves with prime order over a prime field with large embedding factor \cite{boneh1998decision}, specifically DDH holds for the secp256k1 curve, which is used to generate accounts and sign transactions in Bitcoin and Ethereum among other cryptocurrencies.

@@

\begin{enumerate}
	\item $\mathcal{V}$: $s\stackrel{\$}{\leftarrow}\mathbb{Z}_q$, then sends $commit(s)$ 
	\item $\mathcal{P}$: $r\stackrel{\$}{\leftarrow}\mathbb{Z}_q$, then sends $y_1=rG$, $y_2=rB$.
	\item $\mathcal{V}$ opens commitment by sending $s$
	\item $\mathcal{P}$ sends $z=r+as \Mod{q}$
	\item $\mathcal{V}$ checks $zG=y_{1}+sA \Mod{q} \land zB=y_{2}+sC \Mod{q}$
\end{enumerate} 
Note that in the following a non-interactive version of this protocol will only be considered that can be achieved by applying the Fiat-Shamir heuristic.

\subsection{ECDSA with arbitrary generator element}
Elliptic Curve Digital Signature Algorithm (ECDSA) is a key component of MixEth. ECDSA is widely deployed in practice, where in most cases signatures are generated and verified with respect to a fixed generator element of the underlying group \cite{fersch2016provable}. Since all generators are equal from a security point of view, a single generator element is usually fixed in order to promote standardization and assists usability.

However, in MixEth, we deploy a somewhat loosened version of ECDSA, where we allow arbitrary generator elements to be used. Such an extension is indeed needed for withdrawing funds from the mixer, because shuffled public keys remain public keys with respect to non-standardized generator elements. Therefore the usual $\sig$ and $\verify$ algorithms for signing and verifying messages get an additional parameter $G^{'}$, which is not necessarily the standardized generator element. Key generation algorithm works as usual $(pk,sk)\stackrel{\$}{\leftarrow}\kgen(1^{\lambda})$, on the other hand $\sigma\stackrel{\$}{\leftarrow}\sig(G^{'},sk,m)$ and  $0/1\leftarrow \verify(G^{'},pk,\sigma, m)$ accept new generators.

@@

A MixEth contract living on the Ethereum blockchain at $id_{contract}$ address must be initialized with the $amt$ parameter, which denotes the denomination of ether to be mixed.
Every sender must deposit exactly $amt$ ether to a specific public key. Deposits with incorrect ether value or invalid public key are rejected. Public keys in subsequent deposit transactions are written into the $initPubKeys[]$ array.

\subsection{Shuffling period}
After the depositing round, shuffling and challenging rounds are coming after in turns. Each shuffling round is followed by a challenging round when the correctness of the preceding shuffle can be challenged by anyone. If a challenge is accepted, then shuffler's deposit is lost, their shuffle is discarded and shuffling continues from the set of public keys prior to the discarded shuffle. In the course of a shuffle an honest shuffler should multiply all the public keys with a secret multiplier $c$ and then permute all the transformed public keys. Honest shuffler commits to $c$ by sending back to MixEth the new shuffling accumulated constant and the shuffled public keys.

@@

Shuffle is done off-chain, however the result and the updated shuffling accumulated constant is loaded into the MixEth contract enabling anyone to verify the shuffle's correctness and to continue public key shuffling after the corresponding challenging round.

@@

On-chain storage is extremely expensive: it requires $\num[group-separator={,}]{20000}$ gas to store a $256$-bit number, however if a particular storage slot is already taken and one wants to overwrite it with a non-zero element than storing only consumes $\num[group-separator={,}]{5000}$ gas. To minimize on-chain storage costs, only the last two list of shuffled public keys are stored in the MixEth contract's permanent storage. Note that storing only the latest list of shuffled public keys would not be enough, since honest receivers could not prove to the contract that their shuffled public key is compromised unless also the last but first list of shuffled keys is also available for the contract to check the Chaum-Pedersen proof against. Such a storage structure implies that after uploading the new list of shuffled public keys, a challenging period should proceed in order to let receivers check the correctness of the shuffle and whether their shuffled public key is stored in the smart contract. Furthermore we also allow senders to shuffle and deposit new public keys at the same time, meaning that only $3$ on-chain transactions (shuffle, withdraw mixed coins and withdraw shuffling deposit) are sufficient to complete the protocol. We left it as a future work to determine the optimal ratio of mixed coins and shuffling deposits in order to incentivise correct shuffling.

@@

We have also adapted MixEth to operate within a state channel. We wrote the implementation within the guidelines of the Counterfactual framework \cite{coleman2018counterfactual}. This allowed us to delegate the processes of setup, liveness disputes and finalisation to the framework so that we could focus on adapting the application logic. Unlike the on-chain implementation the state channel implementation requires that the set of participants be agreed upon upfront. In state channels each update to the state needs to be signed by all other participants, this means that state channel applications are inherently at least $\mathcal{O}(n)$. To co-ordinate these off-chain updates the Counterfactual framework enforces that all applications be turn based, introducing a turn taker for each turn who may propose a new state. The original MixEth implementation was not turn based so we have adapted the application to this constraint, an example of this adaptation is the challenge round. In the on-chain implementation a time period is allowed during which any participant may challenge, we have adapted this by proceeding turn-based through the participants offering each the chance to either challenge or pass. In the case of a breakdown in cooperation in the channel, a liveness fault, it has been shown that all operations succeeding the cooperation breakdown must proceed on chain\cite{mccorryyou} or be abandoned at some financial cost specified by the application, meaning that if every shuffle were to be succeeded by a challenge round each participant would be forced, by threat this lost deposit, to make an on-chain transaction after each shuffle, incurring $\mathcal{O}(n)$ on chain operations. To mitigate this we removed the challenge after each round and instead introduced a challenge round that takes place after all shuffles have completed, during this round any of the preceding shuffles may be challenged.

Given these adaptations the application proceeds as follows, all participants including senders, shufflers and receivers, deposit funds in a mutli-signature wallet compatible with the Counterfactual framework, they then follow the installation protocols specified by the framework to install the adapted MixEth logic. Afterwards each participant signs a transaction that transfers an equal amount to each withdrawer from the multi-sig, dependent on correct execution of the channelised MixEth application logic. This application logic proceeds as follows: each sender names a public key of a shuffler as in the deposit stage of the on-chain application, then each shuffler takes it in turn to shuffle. After all shuffles have taken place each withdrawer is given a turn to either declare fraud or no-fraud on any shuffle round. Finally each withdrawer then provides proof of ownership by submitting a valid signature on the modified ECDSA scheme. If any of these steps does not occur, or does not occur correctly, the protocol aborts and the conditional transfer does not occur. In this case the perpetrator loses a deposit, either through fraud proof or through failure to take their turn when state is published on-chain. A further modification would be to distribute the slashed deposit to each of the other participants, compensating them for their lost time and the gas costs associated with proving the fault of the other party. Following this protocol the on-chain transactions are now reduced to: one transaction from each participant to deposit funds into the multi-sig, and a set of transactions that send funds from the multi-sig to each of the withdrawers and deposits back to each of the other participants.

\begin{table}[H] 
	\caption{Proof-of-concept implementation gas cost results. Expect further improvements. MixEthChannel refers to the implementation which leverages state channels for shuffling and challenging periods}
	\centering 
	\begin{tabular}{@{\extracolsep{6pt}}lccccc@{}} 	
		\toprule
		\hline
		&Deployment&Deposit&\multicolumn{2}{c}{Shuffle}& Withdraw\\
		\cline{4-5}&&&Shuffle upload&Challenge\\
		\hline
		\midrule
		Möbius \cite{meiklejohn2018mobius}     &$\num[group-separator={,}]{1046027}$&$\num[group-separator={,}]{76123}$&0&0&$\num[group-separator={,}]{335714}$n   \\
		Miximus \cite{miximus2018}&$\num[group-separator={,}]{1751378}$&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
		MixEth&TBD&$\num[group-separator={,}]{99254}$&$\num[group-separator={,}]{138653}+\num[group-separator={,}]{10000}n$&$\num[group-separator={,}]{227563}$&$\num[group-separator={,}]{113265}$  \\
		MixEthChannel&TBD&TBD&0&0&TBD\\
		\bottomrule
	\end{tabular}
	\label{table:gasproperties}
\end{table} 
\newpage
\bibliographystyle{plain}
\bibliography{sample}

>>>>

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{authblk}
\usepackage{booktabs}
\usepackage{ae,aecompl}
%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

@@

\begin{abstract}
Cryptocurrencies enable users to transact pseudonymously with each other without relying on trusted parties or intermediaries. These transactions are recorded in an immutable, publicly verifiable ledger. Due to the ledger's transparent nature, privacy is notably reduced. If the link between users' public key and their physical identity is exposed, their pseudonymity is lost. One way to increase users' privacy is to deploy coin mixing services. In this paper, we present MixEth, which is a trustless coin mixing service. MixEth is more efficient than any current proposed trustless coin tumbler. It requires at most only $3$ on-chain transactions per user and $1$ off-chain message. It achieves strong notions of anonymity and is able to resist denial-of-service attacks. Furthermore the underlying protocol can also be used to efficiently shuffle ballots and cyphertexts in a trustless and decentralized manner.     
\end{abstract}
\keywords{Cryptography, Verifiable shuffle, Ethereum, Privacy, Coin mixer, State Channel}

\section{Introduction}
One of the methods to increase cryptocurrency users' privacy is coin mixing or tumbling. This technique provides \textit{k-anonymity} or \textit{plausible deniability}. The idea is that $k$ users deposit $1$ coin each and then in the course of a coin shuffling protocol either a centralized trusted third party or a smart contract mixes the coins and redistributes them to designated fresh public keys. This powerful technique gives users superior privacy and anonymity since their newly received coins can not be linked to them.

@@

The two major techniques to provide decentralized mixing services for Ethereum are Möbius, a ring-signature-based solution \cite{meiklejohn2018mobius} and Miximus, a zkSNARK-based proposal \cite{miximus2018}. Both of them require usage of a large amount of gas to withdraw funds, which could be prohibitive for many use cases. Möbius requires $\num[group-separator={,}]{335714}n$ gas ($n$ is the ring size) while Miximus consumes $\num[group-separator={,}]{1903305}$ gas to verify a zkSNARK proof \cite{miximus2018gascost}.

\textbf{Our contributions.} In this paper, we present a trustless and efficient mixing protocol for Turing-complete blockchains. To show the practicality of the protocol, we introduce MixEth, a privacy-enhancing protocol and a practical tool for Ethereum. MixEth overcomes the above mentioned efficiency issues of an Ethereum-based coin-mixer while retaining the strong notions of anonymity, mixer availability and theft prevention already achieved by previous proposals (\cite{meiklejohn2018mobius},\cite{miximus2018}). MixEth requires as few off-chain messages and on-chain transactions as Möbius and Miximus, meanwhile it burns significantly less gas.

We also implement MixEth in a state channel to leverage the scalability and instant finality of off-chain scaling solutions.

\section{Background}
\subsection{Notations}
Let $[]$ denote the empty tuple. For a tuple $t=(x_1,\dots,x_n)$ we denote $t[x_i]$ as the value stored at $x_{i}$. The cardinality of a finite set $X$ is denoted as $|X|$. In the following let $\lambda \in \mathbb{N}$ be the security parameter and its unary representation is $1^{\lambda}$. If $x$ is uniformly randomly sampled from a set $A$ we write $x\stackrel{\$}{\leftarrow}A$. The symmetric group of degree $n$ is written as ${S}_n$. In a cyclic group $\mathbb{G}$, the standardized generator is denoted as $G$ and we use the additive notation. Secret keys and public keys are denoted as $sk$ and $pk$ respectively (or often times $s$ and $sG$), while the user the corresponding key belongs to is indicated in subscript. Let $PK_{i}$ denote the set of public keys belonging to receivers at a particular shuffling round $i$.

@@

The Decision Diffie-Hellman assumption (DDH) is a standard cryptographic hardness assumption which underlies the security of many cryptographic protocols. Roughly speaking DDH states that no efficient algorithm can distinguish between the two distributions $(aG, bG, abG)$ and $(aG, bG, cG)$, where $a,b,c\stackrel{\$}{\leftarrow}\mathbb{Z}_{|\mathbb{G}|}$. It is believed that the DDH assumption holds for elliptic curves with prime order over a prime field with large embedding factor \cite{boneh1998decision}, specifically DDH holds for the secp256k1 curve used in Ethereum.

@@

\begin{enumerate}
	\item $\mathcal{V}$: $s\stackrel{\$}{\leftarrow}\mathbb{Z}_q$, then sends $commit(s)$ 
	\item $\mathcal{P}$: $r\stackrel{\$}{\leftarrow}\mathbb{Z}_q$, then sends $y_1=rG$, $y_2=rB$.
	\item $\mathcal{V}$ opens commitment by sending $s$
	\item $\mathcal{P}$ sends $z=r+as \Mod{q}$
	\item $\mathcal{V}$ checks $zG=y_{1}+sA \Mod{q} \land zB=y_{2}+sC \Mod{q}$
\end{enumerate} 
Note that in the following a non-interactive version of this protocol will only be considered. This can be achieved by applying the Fiat-Shamir heuristic.

\subsection{ECDSA with arbitrary generator element}
Elliptic Curve Digital Signature Algorithm (ECDSA) is a key component of MixEth. ECDSA is widely deployed in practice, where in most cases signatures are generated and verified with respect to a fixed generator element of the underlying group \cite{fersch2016provable}. Since all generators are equal from a security point of view, a single generator element is usually fixed in order to promote standardization and assist usability.

However, in MixEth, we require the use of arbitrary generator elements. Such an extension is needed for withdrawing funds from the mixer as the shuffled public keys remain public keys with respect to non-standardized generator elements. Therefore the usual $\sig$ and $\verify$ algorithms for signing and verifying messages require an additional parameter $G^{'}$, which is not necessarily the standardized generator element. Key generation algorithm works as usual $(pk,sk)\stackrel{\$}{\leftarrow}\kgen(1^{\lambda})$, on the other hand $\sigma\stackrel{\$}{\leftarrow}\sig(G^{'},sk,m)$ and  $0/1\leftarrow \verify(G^{'},pk,\sigma, m)$ accept new generators.

@@

A MixEth contract is deployed on the Ethereum blockchain at $id_{contract}$ address and is initialized with the $amt$ parameter which denotes the denomination of ether to be mixed.
Every sender must deposit exactly $amt$ ether to a specific public key. Deposits with incorrect ether value or invalid public key are rejected. Public keys in subsequent deposit transactions are written into the $initPubKeys[]$ array.

\subsection{Shuffling period}
After the depositing round the shuffling and challenging rounds alternate in turn. Each shuffling round is followed by a challenging round where the correctness of the preceding shuffle can be challenged by anyone. If a challenge is accepted, then shuffler's deposit is lost, their shuffle is discarded and shuffling continues from the set of public keys prior to the discarded shuffle. In the course of a shuffle an honest shuffler multiplies all the public keys with a secret multiplier $c$ and then permutes the transformed public keys. This shuffling is done off-chain, then the shuffler commits to $c$ by sending back to MixEth the new shuffling accumulated constant and the shuffled public keys. This allows anyone to verify the shuffle and, if required, submit a challenge during the succeeding challenge round.

@@

@@

On-chain storage is extremely expensive: it requires $\num[group-separator={,}]{20000}$ gas to store a $256$-bit number, however if a particular storage slot is already taken and one wants to overwrite it with a non-zero element than storing only consumes $\num[group-separator={,}]{5000}$ gas. To minimize on-chain storage costs, only the last two list of shuffled public keys are stored in the MixEth contract's permanent storage. Note that storing only the latest list of shuffled public keys would not be enough, since honest receivers could not prove to the contract that their shuffled public key is compromised unless also the last-but-one list of shuffled keys is also available for the contract to check the Chaum-Pedersen proof against. Such a storage structure implies that after uploading the new list of shuffled public keys, a challenging period should proceed in order to let receivers check the correctness of the shuffle and whether their shuffled public key is stored in the smart contract. Furthermore we also allow senders to shuffle and deposit new public keys at the same time, meaning that only $3$ on-chain transactions (shuffle, withdraw mixed coins and withdraw shuffling deposit) are sufficient to complete the protocol. We left it as a future work to determine the optimal ratio of mixed coins and shuffling deposits in order to incentivise correct shuffling.

@@

We have also adapted MixEth to operate within a state channel. We wrote the implementation within the guidelines of the Counterfactual framework \cite{coleman2018counterfactual}. This allowed us to delegate the processes of setup, liveness disputes and finalisation to the framework so that we could focus on adapting the application logic. Unlike the on-chain implementation the state channel implementation requires that the set of participants be agreed upon upfront. In state channels each update to the state needs to be signed by all other participants, this means that state channel applications are inherently at least $\mathcal{O}(n)$. To co-ordinate these off-chain updates the Counterfactual framework enforces that all applications be turn based, introducing a turn taker for each turn who may propose a new state. The original MixEth implementation was not turn based so we have adapted the application to this constraint, an example of this adaptation is the challenge round. In the on-chain implementation a time period is allowed during which any participant may challenge, we have adapted this by proceeding turn-based through the participants offering each the chance to either challenge or pass. In the case of a breakdown in cooperation in the channel, a liveness fault, it has been shown that all operations succeeding the cooperation breakdown must proceed on chain\cite{mccorryyou} or be abandoned at some financial cost specified by the application, meaning that if every shuffle were to be succeeded by a challenge round each participant would be forced, by threat of lost deposit, to make an on-chain transaction after each shuffle, incurring $\mathcal{O}(n)$ on chain operations. To mitigate this we removed the challenge after each round and instead introduced a challenge round that takes place after all shuffles have completed, during this round any of the preceding shuffles may be challenged.

Given these adaptations the application proceeds as follows, all participants including senders, shufflers and receivers, deposit funds in a mutli-signature wallet compatible with the Counterfactual framework, they then follow the installation protocols specified by the framework to install the adapted MixEth logic. Afterwards each participant signs a transaction that transfers an equal amount to each withdrawer from the multi-sig, dependent on correct execution of the channelised MixEth application logic. This application logic proceeds as follows: each sender names a public key of a shuffler as in the deposit stage of the on-chain application, then each shuffler takes it in turn to shuffle. After all shuffles have taken place each withdrawer is given a turn to either declare fraud or no-fraud on any shuffle round. Finally each withdrawer then provides proof of ownership by submitting a valid signature on the modified ECDSA scheme.

If any of these steps does not occur, or does not occur correctly, the protocol aborts and the conditional transfer does not occur. In this case the perpetrator loses a deposit, either through fraud proof or through failure to take their turn when state is published on-chain. A further modification would be to distribute the slashed deposit to each of the other participants, compensating them for their lost time and the gas costs associated with proving the fault of the other party.

Following this protocol the on-chain transactions are now reduced to: one transaction from each participant to deposit funds into the multi-sig, and a set of transactions that send funds from the multi-sig to each of the withdrawers and deposits back to each of the other participants.

\begin{table}[H] 
	\caption{Proof-of-concept implementation gas cost results. MixEthChannel refers to the implementation which leverages state channels for shuffling and challenging periods}
	\centering 
	\begin{tabular}{@{\extracolsep{6pt}}lccccc@{}} 	
		\toprule
		\hline
		&Deployment&Deposit&\multicolumn{2}{c}{Shuffle}& Withdraw\\
		\cline{4-5}&&&Shuffle upload&Challenge\\
		\hline
		\midrule
		Möbius \cite{meiklejohn2018mobius}     &$\num[group-separator={,}]{1046027}$&$\num[group-separator={,}]{76123}$&0&0&$\num[group-separator={,}]{335714}$n   \\
		Miximus \cite{miximus2018}&$\num[group-separator={,}]{1751378}$&$\num[group-separator={,}]{732815}$&0&0 &$\num[group-separator={,}]{1903305}$  \\
		MixEth&TBD&$\num[group-separator={,}]{99254}$&$\num[group-separator={,}]{138653}+\num[group-separator={,}]{10000}n$&$\num[group-separator={,}]{227563}$&$\num[group-separator={,}]{113265}$  \\
		MixEthChannel&TBD&TBD&0&0&TBD\\
		\bottomrule
	\end{tabular}
	\label{table:gasproperties}
\end{table} 
\newpage
\bibliographystyle{plain}
\bibliography{sample}
